---
title: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<br>

## Labs  
Every single day is an experiment - manage and be mindful of the process. #sciencejedi  

[Lab manual](https://figshare.com/articles/An_experimental_design_cookbook/9728204)  

### Dataset and meta-data for pilot experiment 5%  

### Data and meta-data for field experiment 5%  

### Field lab report 30%  
[FACETS](https://www.facetsjournal.com/about/) is Canada’s first and only multidisciplinary open access science journal.  Follow the [instructions](https://www.facetsjournal.com/authors/instructions/) proposed for a **research article** for this journal - 5000 words preferred.  

**Structure of PDF research article**     
Page 1. Title, name, and abstract.  
Page 2-3. Introduction.  
Page 4. Methods.  
Page 5. Results (not including figure, put at end of PDF).    
Page 6. Discussion.  
Page 7. Literature cited.  
Page 8. Figure legend on this page.  
Page 9. Figure on this page.  
Page 10. Acknowledgments.  

Single spaced, 12 point font, at least 1 inch margins (the default).  
PDF format only.  
Lab reports must also be submitted to [turnitin.com](https://www.turnitin.com).   

**Marking key**  
```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(knitr)
schedule <- read_csv("BIOL3250_field_labs.csv")
knitr::kable(schedule)
```

### Data-design lab report 10%  
[FACETS](https://www.facetsjournal.com/about/) is Canada’s first and only multidisciplinary open access science journal.  Follow the [instructions](https://www.facetsjournal.com/authors/instructions/) proposed for a **note** for this journal - 1400 words preferred.  

**Structure of note**  
Page 1. One paragraph Introduction.  
Page 2. One paragraph description of results.  
Page 3. Conclusions and implications of what you found.  



 


