---
title: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<br>  

## Labs  
Every single day is an experiment - manage and be mindful of the process. #sciencejedi  

[Lab manual](http://www.designcraft4experiments.club)  
<br>  

### Dataset and meta-data for pilot experiment 5%  
Collected from one of the field three experiments: bird, bioblitz, or survey.  
```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(knitr)
data<- read_csv("BIOL3250_data.csv")
knitr::kable(data)
``` 

<br>  

### Data and meta-data for field experiment 5%  
Collected for a single field experiment in depth.  
```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(knitr)
data<- read_csv("BIOL3250_data.csv")
knitr::kable(data)
``` 

<br>  

### Field lab report 30%  
Single spaced, 12 point font, at least 1 inch margins (the default).  
PDF format only.  
Lab reports must also be submitted to [turnitin.com](https://www.turnitin.com).  

[FACETS](https://www.facetsjournal.com/about/) is Canada’s first and only multidisciplinary open access science journal.  Follow the [instructions](https://www.facetsjournal.com/authors/instructions/) proposed for a **research article** for this journal - 5000 words preferred.  

```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(knitr)
field <- read_csv("BIOL3250_field_labs.csv")
knitr::kable(field)
```
<br>  

### Data-design lab report 10%  
Single spaced, 12 point font, at least 1 inch margins (the default).  
PDF format only.  
Lab reports must also be submitted to [turnitin.com](https://www.turnitin.com).  

[FACETS](https://www.facetsjournal.com/about/) is Canada’s first and only multidisciplinary open access science journal.  Follow the [instructions](https://www.facetsjournal.com/authors/instructions/) proposed for a **note** for this journal - 1400 words preferred.  

```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(knitr)
design<- read_csv("BIOL3250_data_design_labs.csv")
knitr::kable(design)
```

 


